A Formal Model of Checked C

### 2022-11-22 sandp23/formal.tex

\myparagraph{Constant Validity}
Rules \textsc{T-ConstU} and \textsc{T-ConstC}
describes type assumptions for constants appearing in a program.
$\cmode(\tau)$ judges that a constant pointer 
in an unchecked region cannot be of a checked type,
which represents an assumption that programmers 
cannot guess a checked pointer address and utilize it in an unchecked region in \systemname.
\mz{Or simply a checked pointer is not permitted in an unchecked region? }
In rule \textsc{T-ConstC}, we requires a static 
verification procedure for validating a constant pointer, 
which is similar to the dynamic verification process in \Cref{sec:semantics}. 
\liyi{what dynamic verification process? }

@@

A checked pointer checks validity in type step as rule \textsc{T-ConstC},
while a tainted/unchecked pointer does not check for such during the type checking.
Tainted pointers are verified through the validity check in dynamic execution as we mentioned above.
\liyi{This is saying that the validity checks and verification are the same, but the word ''verification'' could be misleading, so maybe change it? }
\mz{Validation instead? 
  %
  If for this entire section you want to emphasize what constant pointers are
  allowed in some specific regions, validation might be much appropriate.
  % 
  It might also be worth stated at the beginning that you have two kinds of
  validation procedures: static one for checked, and instrumented dynamic checks
  for unchecked region.  }

>>>>

\myparagraph{Constant Validity}
Rules \textsc{T-ConstU} and \textsc{T-ConstC}
describes type assumptions for constants appearing in a program.
$\cmode(\tau)$ judges that a constant pointer 
in an unchecked region cannot be of a checked type,
which represents an assumption that programmers 
cannot guess a checked pointer address and utilize it in an unchecked region in \systemname.
\mz{Or, simply, a checked pointer is not permitted in an unchecked region? }
In rule \textsc{T-ConstC}, we requires a static 
verification procedure for validating a constant pointer, 
which is similar to the dynamic verification process in \Cref{sec:semantics}. 
\liyi{what dynamic verification process? }

@@

A checked pointer checks validity in type step as rule \textsc{T-ConstC},
while a tainted/unchecked pointer does not check for such during the type checking.
Tainted pointers are verified through the validity check in dynamic execution as we mentioned above.
\liyi{This is saying that the validity checks and verification are the same, but the word ''verification'' could be misleading, so maybe change it? }
\mz{Validation instead? 
  %
  If what you want to emphasize is what kind of constant pointers are allowed in
  some specific regions, validation might be more appropriate in these paragraphs.
  % 
  It might also be worth stateing at the beginning that you have two kinds of
  validation procedures: static one for checked, and instrumented dynamic checks
  for unchecked region.  }
